---
title: "Plot Aggregated"
author: "mjiwa"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Install relevant packages (if you haven't already)
# install.packages("here", "stringr", "pracma", "plyr", "dplyr",
#                  "rlang", "ggplot2", "rstatix", "kableExtra",
#                  "scico", "gridExtra", "reshape2")

# Attach packages
library(here)
library(plyr)
library(dplyr)
library(rlang)
library(ggplot2)
library(rstatix)
library(kableExtra)
library(scico)
library(gridExtra)
library(reshape2)

```


```{r import, include=FALSE}

# Load data
source(here::here("analysis", "myProj_readData.R"))

# Make function to return mean and sd of grouped data
data_summary <- function(data, varname, groupnames){
  require(plyr)
  require(dplyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  data_sum <- ddply(data, groupnames, .fun=summary_func,
                  varname)
  names(data_sum)[names(data_sum) == "mean"] <- varname
 return(data_sum)
}

# Create theme for blank axis in ggplot
blank_theme = theme(
  axis.text.y = element_text(size = 10, colour = "black"),
  axis.text.x = element_text(size = 10, colour = "black"),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  axis.line = element_line(colour = "black"),
  legend.position = "none"
)

```


```{css, echo=FALSE}
.center {
  display: table;
  margin-right: auto;
  margin-left: auto;
}
```

## Demographics

### N = `r length(IDs)`, excluded = `r length(excluded)` for failing attention checks.

```{r demographics, echo=FALSE, message=FALSE, fig.height= 3, fig.align = 'center'}

# Make histogram of age data
agePlot <- ggplot(data = demographics, aes(x = Age)) +
  geom_histogram(bins = 8, fill = "#f5cb42", color = "black") +
  xlab("Age") +
  ylab("Count") +
  blank_theme +
  labs(title = "Age") +
  theme(plot.title = element_text(hjust = 0.5))

# Compile counts of gender data
gend <- demographics %>%
  group_by(Gender) %>% 
  dplyr::summarise(n = n())

gend$Gender[gend$Gender == "F"] <- "Female"
gend$Gender[gend$Gender == "M"] <- "Male"
gend$Gender[gend$Gender == "O"] <- "Other"

# Make pie-chart of gender data
genderPlot <- ggplot(data = gend, aes(x = "", y = n, fill = Gender)) +
  geom_bar(stat = "identity", color = "black") +
  coord_polar("y", start = 0) +
  blank_theme +
  labs(title = "Gender",
       fill = "Gender") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.line = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "right",
        axis.ticks = element_blank(),
        panel.border = element_blank())

# Create a grid to display both demographic plots
gridExtra::grid.arrange(agePlot, genderPlot, ncol=2)

```

## Plot by percentage difference

This is a plot of participants' mean bids divided up by the percentage difference between the two response options.

```{r diffPlots, echo=FALSE, message=FALSE, fig.align = 'center'}

# Create summarised data for plotting
temp <- data_summary(allTrials, varname = "bid", groupnames = c("diff"))
temp$se <- temp$sd / sqrt(length(unique(allTrials$ID)))
temp_ind <- data_summary(allTrials, varname = "bid", groupnames = c("ID", "diff"))

# Make barplot with error bars and individual data points
diffPlot <- ggplot(data = temp, aes(x = as.factor(diff), y = bid, fill = as.factor(diff))) +
  geom_bar(colour = "black", size = .5, stat = "identity") +
  scale_fill_scico_d(palette = 'bilbao', begin = .25, end = .75) +
  geom_errorbar(aes(ymin = bid-se, ymax = bid+se), width=.2,
                 position = position_dodge(.9)) +
  geom_jitter(data = temp_ind, aes(x = as.factor(diff), y = bid), 
              width = .25, height = 0) +
  xlab("Difference in Predictors") +
  ylab("Bid") +
  blank_theme
show(diffPlot)

# Make violin plot using the same data
violinDiffPlot <- ggplot(data = temp_ind, 
                         aes(x = as.factor(diff), y = bid)) +
  geom_violin(aes(fill = as.factor(diff))) +
  geom_boxplot(width = 0.1, fill = "black", alpha = .25, outlier.shape = NA) +
  xlab("Difference in Predictors") +
  ylab("Bid") +
  scale_fill_scico_d(palette = 'bilbao', begin = .25, end = .75) +
  blank_theme +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14))
show(violinDiffPlot)

# Do ANOVA
# Convert to tibble with factors, remove SD
temp_ind <- as_tibble(temp_ind) %>%
  convert_as_factor(ID, diff) %>%
  select(-sd)
# Perform ANOVA
diff.aov <- anova_test(data = temp_ind, dv = bid, wid = ID,
                       within = diff)$ANOVA


```
<br>

#### ANOVA results:
<div align="center">
#### *F*(`r diff.aov$DFn`, `r diff.aov$DFd`) = `r diff.aov$F`, *p* = `r diff.aov$p`, $\eta^{2}$ = `r diff.aov$ges`
</div>

#### Pairwise comparisons:

```{r diff_pwc, echo=FALSE, message=FALSE}

diff.pwc <- temp_ind %>%
  pairwise_t_test(
    bid ~ diff, paired = TRUE,
    p.adjust.method = "holm"
    )

diff.pwc.frmt <- as_tibble(diff.pwc) %>% 
  # Reformat numbers
  mutate(statistic = abs(round(statistic, 2))) %>% 
  # Rename columns
  dplyr::rename(diff_A = group1, diff_B = group2, `t-statistic` = statistic,
                Outcome = .y., N = n1, `Adjusted p` = p.adj) %>%
  # Remove columns
  select(-c(p.adj.signif, n2))

knitr::kable((diff.pwc.frmt[,]), col.names = colnames(diff.pwc.frmt), 
             row.names = 0) %>%
  kable_styling(font_size = 14, latex_options = "hold_position") %>%
  kableExtra::column_spec(1:8, background = 
                         ifelse(diff.pwc.frmt$`Adjusted p` > .05, 
                                  "#ebc0c0", "#caebca")) %>%  # red, green
 row_spec(c(1:6)[diff.pwc.frmt$p < .05 & diff.pwc.frmt$`Adjusted p` > .05],
          background = "#f2e7b6")


```

<br>
<hr style="border:2px solid gainsboro"> </hr>

## Plot by final colour

#### Plots are divided by whether the final (50% reliable) predictor supported the dominant colour (i.e., colour with the higher reliability) or the non-dominant colour.

Trials with 0 percentage difference were removed from the following analyses.


```{r finalColPlots, echo=FALSE, message=FALSE, fig.align = 'center'}

# Remove 0-diff trials
tempTrials <- allTrials[allTrials$diff != 0,]
temp <- data_summary(tempTrials, varname = "bid", groupnames = c("finalCol"))
temp$se <- temp$sd / sqrt(length(unique(allTrials$ID)))
temp_ind <- data_summary(tempTrials, varname = "bid", groupnames = c("ID", "finalCol"))


finalColPlot <- ggplot(data = temp, aes(x = as.factor(finalCol), y = bid, fill = as.factor(finalCol))) +
  geom_bar(colour = "black", size = .5, stat = "identity") +
  scale_fill_scico_d(palette = 'devon', begin = .25, end = .75) +
  geom_errorbar(aes(ymin = bid-se, ymax = bid+se), width=.2,
                 position = position_dodge(.9)) +
  geom_jitter(data = temp_ind, aes(x = as.factor(finalCol), y = bid), 
              width = .25, height = 0) +
  scale_x_discrete(labels = c("Non-dominant", "Dominant")) +
  xlab("Final Colour") +
  ylab("Bid") +
  blank_theme
show(finalColPlot)

violinFinalColPlot <- ggplot(data = temp_ind, 
                         aes(x = as.factor(finalCol), y = bid)) +
  geom_violin(aes(fill = as.factor(finalCol))) +
  geom_boxplot(width = 0.1, fill = "black", alpha = .25, outlier.shape = NA) +
  xlab("Difference in Predictors") +
  ylab("Bid") +
  scale_x_discrete(labels = c("Non-dominant", "Dominant")) +
  scale_fill_scico_d(palette = 'devon', begin = .25, end = .75) +
  blank_theme +
  theme(axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title = element_text(size = 14))
show(violinFinalColPlot)

```


## Plot by difference and final colour

```{r finalColDiffPlots, echo=FALSE, message=FALSE, fig.align = 'center'}

# Remove 0-diff trials
tempTrials <- allTrials[allTrials$diff != 0,]
temp <- data_summary(tempTrials, varname = "bid", 
                     groupnames = c("diff", "finalCol"))
temp$se <- temp$sd / sqrt(length(unique(allTrials$ID)))
temp_ind <- data_summary(tempTrials, varname = "bid", 
                         groupnames = c("ID", "diff", "finalCol"))


finalColDiffPlot <- ggplot(data = temp, aes(x = as.factor(diff), 
                                            y = bid, fill = as.factor(finalCol))) +
  geom_bar(colour = "black", size = .5, position = "dodge", stat = "identity") +
  geom_errorbar(aes(ymin = bid-se, ymax = bid+se), width=.2,
                 position = position_dodge(.9)) +
  geom_jitter(data = temp_ind, shape = 21, aes(x = as.factor(diff), 
                                                      y = bid, 
                                                      fill = as.factor(finalCol)), 
              colour = "black", size = 2, 
              position = position_jitterdodge(dodge.width = .9, 
                                              jitter.width = .5)) +
  xlab("Difference in Predictors") +
  ylab("Bid") +
  blank_theme +
  theme(legend.position = "right") + 
  scale_fill_manual(name ="Final Colour",
                    labels = c("Non-dominant", "Dominant"), 
                    values = c("#D00000", "#3CD000"))
show(finalColDiffPlot)

```



